Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2014-09-25 paper/paper.tex
Add description for SPSS example schedule

The resulting schedule produced by SPSS algorithm is shown in Fig.~\ref{fig:algorithms-example-spss}.

\begin{figure}[htb] 
  \centering
  \includegraphics[width=0.80\columnwidth]{figures/algorithms-example-spss}
  \caption{Schedule produced by DPDS algorithm for the example ensemble from Figure~\ref{fig:example-ensemble}.
  Workflows a and c complete within the deadline.}
  \label{fig:algorithms-example-spss}
\end{figure}

>>>>

The resulting schedule produced by SPSS algorithm is shown in
Fig.~\ref{fig:algorithms-example-spss}. SPSS generates the schedule by
considering workflows in priority order. It first considers workflow $a$, and
develops a schedule that completes $a$ by its deadline using the minimum
number of node-hours. Once $a$ has been scheduled, SPSS will develop a
low-cost schedule that includes workflow $b$. However, after adding $b$,
the algorithm will determine that the total cost of the combined schedule
for $a$ and $b$ is greater than the budget, and will reject workflow $b$ and
remove it from the schedule. It will then consider workflow $c$, and develop
a low-cost schedule that adds $c$ to the existing schedule for $a$. In order
to complete each job in $c$ by its deadline, SPSS provisions 6 additional
VM-hours. The resulting schedule has a total cost of 16 VM-hours, or
\$16, which is less than the budget of \$18 and completes both $a$ and $c$ by
their deadlines.

\begin{figure}[htb] 
  \centering
  \includegraphics[width=0.80\columnwidth]{figures/algorithms-example-spss}
  \caption{Schedule produced by SPSS algorithm for the example ensemble from Figure~\ref{fig:example-ensemble}.
  Workflows $a$ and $c$ complete within the given budget and deadline.}
  \label{fig:algorithms-example-spss}
\end{figure}
